upwell_IDX

### 2019-08-14 upwell_IDX.Rmd
ud

         exceed = purrr::map(clim, exceedance, minDuration = 3, threshold = 1)) %>% 

@@

  res <- detect_event(df, threshClim2 = df$exceedance, minDuration = 3, coldSpells = T)

@@

  mutate(clim = purrr::map(data, ts2clm, pctile = 30, climatologyPeriod = c("1995-01-01", "2004-12-31"))) %>%

>>>>

         exceed = purrr::map(clim, exceedance, minDuration = 2, threshold = 1)) %>% 

@@

  res <- detect_event(df, threshClim2 = df$exceedance, minDuration = 2, coldSpells = T)

@@

  mutate(clim = purrr::map(data, ts2clm, pctile = 20, climatologyPeriod = c("1995-01-01", "2004-12-31"))) %>%
